%Resumen

\chapter{Abstract}
\markboth{Abstract}{}

{\setlength{\leftskip}{10mm}
\setlength{\parindent}{-10mm}

\autor.

Candidato para obtener el grado de \grado\orientacion.

\uanl.

\fime.

Título del estudio: \textsc{\titulo}.

\noindent Número de páginas: \pageref*{lastpage}.}

%%% Comienza a llenar aquí
\paragraph{Problem Description:}
When a traffic accident occurs
in cities with a large traffic flow
the roads surrounding the crash site
are affected by traffic congestion.
In some countries, such as Mexico,
even small accidents are troublesome
due to the fact
that a claim adjuster
from the car insurance company
must arrive to the site
and document the accident
before the vehicle may be removed
as required by law.
Thus,
in this particular setting,
the location of the adjusters
becomes a key factor in providing timely service.

\paragraph{Objectives and method of study:}
%Aquí debes poner tus objetivos y métodos de estudio.
The propouses of this thesis is to
\begin{itemize}
\item Provide quantitative tools
for scientific support
for the optimal location
of car wreck adjusters.
\item Develop
adequate mathematical models
for representing
some of the important company concerns.
Design and develop efficient solution techniques
for handling real-world instances of the problem.
\item Assess
the quality and value of the proposed techniques
based on an appropriate experimental design.
\end{itemize}

\paragraph{Contributions and Conclusions:}
%Y aquí tus contribuciones y conclusiones.
%(También es parte del formato).
The most important contributions of this work
are listed below:
\begin{itemize}
\item With the aim of
  minimizing average response time,
  two integer programming models
  are introduced.
\item The second model
  make special considerations to
  reduce the number of variables.
\item An scatter search heuristic
  was designed, built and tested
  over a wide set of instances
  with very good results.
\end{itemize}

\bigskip\noindent\begin{tabular}{lc}
\vspace*{-2mm}\hspace*{-2mm}Firma del asesor: & \\
\cline{2-2} & \hspace*{1em}\asesor\hspace*{1em}
\end{tabular}


