\section{Proposed Metaheuristic}
The Scatter Search (SS)
is an evolutionary approach
introduced by Glover \cite{glover1977heuristics}
as a metaheuristic for integer programming.
It is based on diversifying the search
through the solution space.
It operates on a set of solutions,
named the Reference Set,
formed by good and diverse solutions of the main population.
These solutions are combined
with the aim of generate
new solutions with better fitness,
while maintaining diversity.
The General Scheme can be seen in Figure \ref{fig:SS_GS}.
\input{HeuristicProcedures/fig-GeneralScheme}

\subsection{Diversity of a Solution}
% La diversidad de mide respecto al conjunto de referencia actual
The diversity of a solution,
is measured relative to the Reference Set;
% Se usa el perfect matching para calcular el costo
the perfect matching
is evaluated
with each one of the solutions in the Reference Set,
where the cost consist in
the sum of the distances
from each server of the given solution
and their match in the solution of the Reference Set.
% Se utiliza el minimo costo como medida de diversidad
The minimum cost perfect matching
is used as diversity value.
%\todo{Explicar como se calcula la diversidad}

\subsection{Scatter Search}
Scatter-Search metaheuristic
with a dynamic reference set
and a path relinking
as a combination method
was implemented.
We opted for a dynamic reference set
because the number of solutions generated
in each combination is very large.
To enhance the solutions
two improvement methods are included,
one proposed by Berman \cite{berman1987stochastic},
and a local search method
proposed in this research.
%\todo[inline]{Agregar background de Scatter Search}

The pseudocode
of the overall proposed scatter search metaheuristic
is shown in Algorithm \ref{alg:SSInitial}.

The initial step
is to generate the initial population
which is stored in the Reference Set.
This is depicted in Algorithm \ref{alg:SSInitial}.
The cardinality of the reference set is \textit{2b}
(for a given \textit{b}),
consisting of the bests \textit{b} solutions
by objetive function value
and the \textit{b} most diverse solutions.
%%Pendiente revisar si no reemplaza definicion de diversidad previa
%To measute the ``distance''
%between any two solutions,
%we used the value of the minimum perfect matching
%between the corresponding center sets
%of the two solutions.

\input{HeuristicProcedures/alg_ss-template_init}

In Algorithm \ref{alg:SSPhase} (see below),
each pair of solutions
is combined using path relinking procedure.
Because
the Reference Set is dynamic
some pairs are not be combined.
This is due the fact
that some solutions
are removed from the set
before trying to combine them.
\input{HeuristicProcedures/alg_ss-template_phase}
