\section{Queueing Models}
The hypercube model (denoted Hypercube)
and the hypercube approximation (denoted A-Hypercube),
developed by Larson  \cite{larson1974hypercube,larson1975approximating},
are the most well known queueing approaches.
\todo{Explicar para que sirven estos modelos}
for addressing ... %pendiente: Nota de RZRM
%and extended by others (see Swersey \cite{swersey1994deployment})
\todo{Remover extracto}
% source: galvao2008emergency
These are not optimization models,
but they are descriptive models
that permit the analysis of scenarios.
Both models
estimate system operating characteristics
that are used to evaluate a series of objectives.
They can evaluate cooperation between vehicles.
Some of their limitations are:
\begin{itemize}
\item assumptions of an exponentially distributed service time,
\item computational difficulties for problems with many vehicles,
\item require that service time be only vehicle-dependent
  rather than call location-dependent.
\end{itemize}

The computational issues
present in the Hypercube
are addressed in the A-Hypercube.
The vehicle busy probabilities
are dealt with
by solving a system of nonlinear equations
whose size
depends on the number of vehicles.

Optimization models for locating Emergency Medical Services (EMS)
that use Hypercube or A-Hypercube as a function evaluation subroutine
include Jarvis' location-allocation problem \cite{jarvis1975optimization},
Berman and Larson's congested median problem \cite{berman1982median},
Benviniste's location-allocation problem \cite{benveniste1985solving},
and Berman, Larson and Parkan's
stochastic queue p-median problem \cite{berman1987stochastic}.
These methods are heuristic local improvement approaches
that assume it is possible to locate a vehicle in every zone.

\subsection{Mean Service Calibration}
% source: goldber1990simulation
\todo{Remover extracto}
% Hipercubo y A-Hipercubo requieren tiempo dependiente de vehiculo
% tiempo dependiente de llamada puede modelarse con MSC 
Call location-dependent service time
can be modeled using the Mean Service Calibration method (denoted MSC).
% Jarvis y Halpern dan casos donde MST es suficiente para obtener estimaciones
As in Jarvis \cite{jarvis1975optimization} 
and Halpern \cite{halpern1977accuracy}
where
mean service time,
is sufficient
to obtain accurate estimates of system performance.
% en oposicion a
%%as opposed to the distribution of service time,
%%\todo{Corregir para que se entienda}
The major shortcoming of MSC is that either
Hypercube or A-Hypercube
is evaluated in each iteration;
can thus be a computationally expensive approach.

To eliminate the computational inefficiency of the MSC method,
Jarvis \cite{jarvis1985approximating} developed
an approximation model
for spatially distributed queueing systems
(see Appendix \ref{ch:Jarvis}).
The model assumes that call service time
is call location-dependent,
where all vehicles
have the same service rate and utilization
while service is exponentially distributed.

% eof
\subsection{Calibration Process}
% source: galvao2008emergency
% Calibration process of the mean service times
In certain EMSs
and other emergency systems,
travel times may represent
a considerable part of service times.
In such cases,
it may be advisable
to adjust the service times
by means of a calibration process,
which can be performed
using a simple iterative procedure
proposed by Berman et al. \cite{berman1987stochastic}.
Basically,
the procedure consists on
verifying
if there are
significant differences among the input mean service times
and the output mean service times (computed by the hypercube model).
In this case,
the hypercube is solved
using the computed mean service times as inputs,
until
the differences
among input and output values
are sufficiently small.
This procedure is called
a calibration process.
Note that
this procedure takes into account
that the mean travel time
depends on the location of the user
and the identity of the server.
Empirical experiments show
that this procedure
usually converges in two or three iterations,
for a reasonably accurate estimation of the mean service times,
although a formal proof of the convergence of the method
is apparently not available in the literature.
